О множествах точек на плоскости с целочисленными расстояниями

### 2019-05-30 pps-linear-bound/pps-linear-lower-bound.tex
The remaining fixes of iteration

\begin{definition}
	A $\rho(k,M_1 M_2)$-curve, where $-|M_1 M_2| < k < |M_1 M_2|$ and $k$ is integer, is the set of points $N$,
	such that for given points $M_1$ and $M_2$
	the equality $|N M_1| - |N M_2|$ holds.
\end{definition}
So, $\rho(k,M_1 M_2)$-curve is a branch of a hyperbola for $k\neq 0$ and the bisector of line segment $M_1 M_2$ for $k=0$.

>>>>

\begin{definition}
	A $\rho(k,M_1 M_2)$-curve, where $-|M_1 M_2| < k < |M_1 M_2|$ and $k$ is integer, is the set of points $N$,
	such that for given points $M_1$ and $M_2$
	the equality $|N M_1| - |N M_2| = k$ holds.
\end{definition}
So, a $\rho(k,M_1 M_2)$-curve is a branch of a hyperbola for $k\neq 0$ and the bisector of line segment $M_1 M_2$ for $k=0$.
